Review and comparison of tools for managing X.509 certificates and keys

### 2017-01-11 TEX/draft.tex
Final, added key length to GnuPG and Sources

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                              & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool}        & \begin{tabular}[c]{@{}c@{}}     self-signed certificate\end{tabular} &   CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                         & \cellcolor[HTML]{FE0000}No                                           & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000} No & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
Keystore explorer             & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                           & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuTLS                        & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Makecert and pvk2pfx          & \cellcolor[HTML]{34FF34}Yes					     & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Windows PowerShell PKI Module & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Certificate Signing Request}
Possible by using \verb+gpgsm --gen-key > <output_file>+ command, but private key is not a part of output CSR.     
\section{Note}
GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure, that does not include a private key within itself.

\chapter{Keystore Explorer}

@@

>>>>

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                              & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool}        & \begin{tabular}[c]{@{}c@{}}     self-signed certificate\end{tabular} &   CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                         & \cellcolor[HTML]{FE0000}No                                           & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
Keystore explorer             & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                           & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuTLS                        & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Makecert and pvk2pfx          & \cellcolor[HTML]{34FF34}Yes					     & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Windows PowerShell PKI Module & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Certificate Signing Request}
Possible by using \verb+gpgsm --gen-key > <output_file>+ command, but private key is not a part of output CSR.     
\section{Note}
GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure, that does not include a private key within itself.
	\paragraph{Specify Length}
While choosing of key length is avaliable in GnuPG, using \verb+4096bit+ length freezes gpgsm. \verb+2048bit+ and \verb+1024bit+ is however fine.
\chapter{Keystore Explorer}

@@

\chapter{Sources}
For all of the tools where manual pages or help command were avaliable I used them. Besize that I used only a couple of documents and websites: 
\begin{itemize}
 \item \textbf{General} 
   \begin{enumerate}
    \item \href{https://tools.ietf.org/rfc/rfc5280.txt}{RFC 5280}
    \item \href{https://books.google.cz/books/about/Digital_Certificates.html?id=0_3XAAAAMAAJ}{Digital Certificates: Applied Internet Security}
   \end{enumerate}

 \item \textbf{OpenSSL} 
    \begin{enumerate} 
      \item Manual Pages \verb+man <command || option>+
      \item \href{http://operational.io/openssl-commonly-used-commands/}{List of most used OpenSSL commands}
      \item \href{https://jamielinux.com/docs/openssl-certificate-authority/index.html}{Basic tutorial on establishing CA structure}
      \item \href{https://books.google.cz/books?id=IIqwAy4qEl0C&pg=PT4&lpg=PT4&dq=978-0-596-00270-1&source=bl&ots=mb74-Q3DXs&sig=RDQA26zKltVYA1_5PTSkd2tk-Ag&hl=sk&sa=X&ved=0ahUKEwj-mcT4wLrRAhWbIFAKHQcDAaYQ6AEIGTAA#v=onepage&q=978-0-596-00270-1&f=false}{Network Security with OpenSSL By John Viega, Matt Messier, Pravir Chandra}
    \end{enumerate}
 \item{Keytool}
    \begin{enumerate}
     \item \href{http://docs.oracle.com/javase/7/docs/technotes/tools/solaris/keytool.html}{Documentation to keytool from Oracle}
    \end{enumerate}
 \item{GnuPG}
  \begin{enumerate}
   \item \verb+gpgsm --help+ option
   \item \href{https://lists.gnupg.org/pipermail/gnupg-devel/2011-March/025989.html}{Public mailing list}
  \end{enumerate}
 \item{Keystore Explorer}
  \begin{enumerate}
   \item \href{http://help.farnedi.it/wp-content/uploads/2014/08/Generate_Keystore_with_KeyStore_Explorer.pdf}{Keystore Generating Tutorial}
  \end{enumerate}
 \item{XCA}
  \begin{enumerate}
   \item \href{http://xca.sourceforge.net/xca.html}{XCA Sourceforge guide and options}
  \end{enumerate}
 \item{GnuTLS}
  \begin{enumerate}
   \item \href{https://www.gnutls.org/manual/html_node/certtool-Invocation.html}{GnuTLS manual}
  \end{enumerate}
 \item{Makecert and pvk2pfx}
  \begin{enumerate}
   \item \href{https://msdn.microsoft.com/en-us/library/windows/desktop/aa386968(v=vs.85).aspx}{Microsoft's Makecert MSDN page}
   \item \href{https://msdn.microsoft.com/en-us/library/bfsktky3(VS.100).aspx}{Microsoft page dedicated to use of Makecert.exe}
   \item \href{https://blog.jayway.com/2014/09/03/creating-self-signed-certificates-with-makecert-exe-for-development/}{Tutorial on creating self-signed certificate with makecert}
  \end{enumerate}
 \item{Windows PowerShell PKI Module}
  \begin{enumerate}
   \item \href{https://technet.microsoft.com/en-us/library/hh848633.aspx}{Microsoft's page on New-SelfSignedCertificate}
   \item \href{http://windowsitpro.com/blog/creating-self-signed-certificates-powershell}{Tutorial on creating self-signed certificate via PowerShell}
   \item \href{http://woshub.com/how-to-create-self-signed-certificate-with-powershell/}{Another tutorial on creating self-signed certificate}
  \end{enumerate}

\end{itemize}
